### 2018-07-17 latex/discussion.tex
Some changes from AE to BE

Our findings shed new light on the potential physiological role of NNMT, which has earlier been recognized as potential marker for some types of cancer \citep[e.g.][]{Okamura1998}. The main healthy tissue expressing NNMT is the liver, while no or only little expression of NNMT is observed in most other healthy tissues \citep{Aksoy1994}. The increased NNMT expression observed in some types of cancer, might serve to remove Nam derived by increased NAD-dependent signalling. To maintain high NAD concentrations, a simultaneous higher expression of NamPRT is required, which is what has been found in some types of cancer \citep{Bi2011,Wang2011}. It is worth noticing, that NNMT is only advantageous as long as NamPRT affinity is sufficiently high. This suggests that certain types of cancer expressing NNMT at a high level, would potentially be more susceptible to competitive inhibitors of NamPRT. Several of such inhibitors are currently tested in clinical studies \citep{EspindolaNetto2017,Xu2015SR}. Based on our analysis, we would suggest that it might be reasonable to screen patients before treatment, as non-NNMT expressing tumours might respond less to competitive NamPRT inhibitors and missing Nam degradation in those cancer cells would potentially lead to an accumulation of Nam that could outcompete the inhibitor. The latter aspect is not well investigated and requires further analysis.

>>>>

Our findings shed new light on the potential physiological role of NNMT, which has earlier been recognised as potential marker for some types of cancer \citep[e.g.][]{Okamura1998}. The main healthy tissue expressing NNMT is the liver, while no or only little expression of NNMT is observed in most other healthy tissues \citep{Aksoy1994}. The increased NNMT expression observed in some types of cancer, might serve to remove Nam derived by increased NAD-dependent signalling. To maintain high NAD concentrations, a simultaneous higher expression of NamPRT is required, which is what has been found in some types of cancer \citep{Bi2011,Wang2011}. It is worth noticing, that NNMT is only advantageous as long as NamPRT affinity is sufficiently high. This suggests that certain types of cancer expressing NNMT at a high level, would potentially be more susceptible to competitive inhibitors of NamPRT. Several of such inhibitors are currently tested in clinical studies \citep{EspindolaNetto2017,Xu2015SR}. Based on our analysis, we would suggest that it might be reasonable to screen patients before treatment, as non-NNMT expressing tumours might respond less to competitive NamPRT inhibitors and missing Nam degradation in those cancer cells would potentially lead to an accumulation of Nam that could outcompete the inhibitor. The latter aspect is not well investigated and requires further analysis.

### 2018-07-17 latex/figurelegends.tex
Some changes from AE to BE

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig_8_evo_events}
  \caption{\textbf{Schematic representation of evolutionary events in the NAD pathway.} Based on the phylogenetic analysis presented here (roman font) and earlier work \cite{Lau2010} (italic font) we summarized and indicated important events in the evolution of NAD metabolism in Metazoa.}
  \label{fig:evo_events}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig_8_evo_events}
  \caption{\textbf{Schematic representation of evolutionary events in the NAD pathway.} Based on the phylogenetic analysis presented here (roman font) and earlier work \cite{Lau2010} (italic font) we summarised and indicated important events in the evolution of NAD metabolism in Metazoa.}
  \label{fig:evo_events}
\end{figure}

### 2018-07-17 latex/results.tex
Some changes from AE to BE

\subsection{Functional properties of NamPRT and NNMT have evolved to maximize NAD-dependent signalling}

To resolve this apparent contradiction, we wished to scrutinize the NAD metabolic network. Given the complexity of this network, we turned to modelling approaches and built a dynamic model of NAD metabolism based on previously reported kinetic data (for details, see experimental procedures and suppl. tab.~S2).

>>>>

\subsection{Functional properties of NamPRT and NNMT have evolved to maximise NAD-dependent signalling}

To resolve this apparent contradiction, we wished to scrutinise the NAD metabolic network. Given the complexity of this network, we turned to modelling approaches and built a dynamic model of NAD metabolism based on previously reported kinetic data (for details, see experimental procedures and suppl. tab.~S2).
